\documentclass[letterpaper]{article}%
\input{tex-util/misc.tex}
\input{tex-util/figures.tex}
\input{tex-util/homeworks.tex}
\input{tex-util/listings.tex}
\input{tex-util/math.tex}
\input{tex-util/pagesetup.tex}

\def\CourseTitle{Advanced Database Systems}
\def\CourseNumber{CSCI-GA.2434-001}
\def\Instructor{Prof. Dennis Shasha}
\def\HomeworkSetNumber{2}

\author{%
  Brandon Reiss \& Kevin Mullin
}

\date{Tuesday, November 19th, 2013}
\title{%
  \CourseTitle{} - Homework \HomeworkSetNumber{} \\
  {\large \Instructor{}} \\
  {\large \CourseNumber{}}
}

\lhead{\CourseNumber{} - Problem Set \HomeworkSetNumber{}}
\chead{}
\rhead{Reiss \& Mullin, \thepage{} of \pageref{LastPage}}
\fancyfoot{}

\begin{document}
\noindent
\maketitle
\thispagestyle{empty}

\begin{problemcopy}
ReserveWithUs is an electronic portal for hotel rooms. It buys rooms at
discounted rates and sells them for a bit more (see hotels.com for a real-life
model of such a company). The company is composed of a purchasing department
that negotiates deals with hotels and a sales department that monitors customer
activities. Each hotel has a few types of room (e.g., superior, king, queen).
For each type of room in a given hotel, the purchasing department negotiates a
block of rooms of a given type at a given price on a given day. Potential
customers browse the web site to find attractive hotels and room deals.
Possibly, they log in and add a (number of) rooms to their shopping cart.
Customers can then buy all the rooms in their shopping cart, a so-called
shopping cart checkout, where the information about the booked rooms are
committed to the database and archived. You are the IT person at ReserveWithUs
and you have been given a simple application server. The application server is
written in Java (tested on Java 1.6). The application server together with the
database schema and scripts to generate data is available at
http://code.google.com/p/databasetuning-cases/. The design of the application
server is described on that web site. The source code is available and you
should take some time to familiarize yourself with it.

Your job is to tune the database portion of the application in your environment
and to redesign some portions of the application server that are poorly
designed. Specifically, your project is to document the following tasks (back
up your claims with arguments where possible with quantitative arguments based
on experiments):
\end{problemcopy}

\section{Introduction}
\subsection{Environment Setup}
\section{Tuning}
\subsection{Query on hotel and room based on country and city}

\end{document}

